---
title: "Do Digital Nudges Survive Complexity? Analysis Code"
output: html_document
---

```{r setup, message = FALSE}
knitr::opts_chunk$set(echo = TRUE, comment = NA)
options(width = 140)
suppressPackageStartupMessages({ library(sandwich); library(lmtest); library(nnet) })

load(file.path("data", "cleaned_data.rda"))   # wide, long (from data_cleaning.R)

bhs  <- c("BUY", "HOLD", "SELL")
arms <- c(NO_AI = "No AI", NEUTRAL_AI = "Neutral AI", BIASED_AI = "Biased AI", DEBIASED_AI = "Debiasing AI")
star <- function(p) ifelse(is.na(p), "", ifelse(p < .001, "***", ifelse(p < .01, "**",
                    ifelse(p < .05, "*", ifelse(p < .1, ".", "")))))
clp  <- function(fit, cluster) coeftest(fit, vcov = vcovCL, cluster = cluster)
num_sum <- function(x) { x <- suppressWarnings(as.numeric(x)); x <- x[is.finite(x)]
  c(Mean = mean(x), Median = median(x), SD = sd(x), Min = min(x), Max = max(x),
    IQR = as.numeric(diff(quantile(x, c(.25, .75)))), n = length(x)) }

# participant covariates used in the regressions
cov <- data.frame(participant_id = wide$participant_id, risk = wide$risk_tolerance,
                  chartc = wide$chart_comfort, invested = ifelse(wide$investment_exp == "Yes", "Yes", "No"))
```

# 3. Experimental Design

## 3.2 Sample and Recruitment

```{r sample-quality}
data.frame(Measure = c("Participants", "Completed all rounds and the closing questionnaire",
                       "Completed round 5, skipped the closing questionnaire", "Stopped after round 4",
                       "Experimental rounds", "Time Limit rounds with an expired timer (scored as Hold)",
                       "Passed the Hold attention item", "Passed all three checks",
                       "Quality score 80 or above", "Quality score 75 to 79"),
           Value = c(nrow(wide), sum(wide$completed), sum(!wide$completed & !is.na(wide$round5_action)),
                     sum(is.na(wide$round5_action)), nrow(long), sum(long$timed_out),
                     sum(wide$attn_hold_pass), sum(wide$n_attn_passed == 3),
                     sum(wide$quality_score >= 80), sum(wide$quality_score >= 75 & wide$quality_score < 80)))
```

# 4. Empirical Results

## 4.1 Sample Overview, Balance Verification and Engagement

### Table 2: Sample Baseline Characteristics and Randomization Balance

```{r table2}
ai_f <- factor(wide$session_ai_condition, levels = names(arms))
fmtp <- function(p) if (p < .001) "<.001" else sprintf("%.3f", p)
num_row <- function(label, x) {
  per <- tapply(x, ai_f, function(v) sprintf("%.1f (%.1f)", mean(v, na.rm = TRUE), sd(v, na.rm = TRUE)))
  data.frame(Characteristic = label, Overall = sprintf("%.1f (%.1f)", mean(x, na.rm = TRUE), sd(x, na.rm = TRUE)),
             t(per), p = fmtp(summary(aov(x ~ ai_f))[[1]][["Pr(>F)"]][1]), check.names = FALSE) }
pct_row <- function(label, ind) {
  per <- tapply(ind, ai_f, function(v) sprintf("%.0f%%", 100 * mean(v)))
  data.frame(Characteristic = label, Overall = sprintf("%.0f%%", 100 * mean(ind)), t(per),
             p = fmtp(suppressWarnings(chisq.test(table(ind, ai_f))$p.value)), check.names = FALSE) }
t2 <- rbind(
  num_row("Age (years, band midpoint), M (SD)", wide$age_num),
  pct_row("Female, %", wide$gender %in% "Female"),
  pct_row("Postgraduate (Master's/PhD), %", wide$education %in% c("Master's", "PhD")),
  pct_row("Business/Economics or STEM, %", wide$field %in% c("Business / Economics", "STEM")),
  pct_row("Employed / self-employed, %", wide$employment %in% c("Employed", "Self-employed / Business owner")),
  pct_row("Invested before, %", wide$investment_exp == "Yes"),
  num_row("Chart comfort (1-5), M (SD)", wide$chart_comfort),
  num_row("Risk tolerance (1-5), M (SD)", wide$risk_tolerance),
  num_row("Preference for quick decisions (1-5), M (SD)", wide$quick_decisions))
names(t2)[3:6] <- arms
table(ai_f)
t2
```

### Decision Times and Engagement (Figure 2)

```{r engagement}
nt <- long[long$condition != "time_limit", ]          # Time Limit rounds: 15-second timer, assistant disabled
c(median_round = median(nt$decision_sec, na.rm = TRUE),
  median_with_ai_query = median(nt$decision_sec[nt$asked_ai_round], na.rm = TRUE),
  median_without_ai_query = median(nt$decision_sec[!nt$asked_ai_round], na.rm = TRUE))

# per-participant median decision time by AI group (Figure 2b)
pp <- aggregate(decision_sec ~ participant_id + ai_condition, nt, median)
tapply(pp$decision_sec, pp$ai_condition, median)
kruskal.test(decision_sec ~ ai_condition, pp)$p.value
pairwise.wilcox.test(pp$decision_sec, pp$ai_condition, p.adjust.method = "BH")

# by round, assistant vs no assistant (Figure 2a)
nt$grp <- ifelse(nt$ai_condition == "NO_AI", "No AI", "AI assistant")
fr <- aggregate(cbind(median_sec = decision_sec) ~ grp + round, nt[is.finite(nt$decision_sec), ], median)
fr$hold_share   <- aggregate(action == "HOLD" ~ grp + round, nt[is.finite(nt$decision_sec), ], mean)[, 3]
fr$target_share <- aggregate(on_target ~ grp + round, nt[is.finite(nt$decision_sec), ], mean)[, 3]
fr$ai_query     <- aggregate(asked_ai_round ~ grp + round, nt[is.finite(nt$decision_sec), ], mean)[, 3]
fr[order(fr$grp, fr$round), ]

# session duration (minutes): overall and by AI group
median(wide$completion_time_min, na.rm = TRUE)
tapply(wide$completion_time_min, wide$session_ai_condition, median, na.rm = TRUE)

# in-task confidence and AI attitudes
colMeans(wide[c("round2_confidence", "round4_confidence")], na.rm = TRUE)
colMeans(wide[c("ai_trust", "ai_predictable", "ai_comfort")], na.rm = TRUE)

# baseline-round choice shares (%)
round(100 * prop.table(table(factor(wide$baseline_action, levels = bhs))), 1)
```

## 4.2 Primary Effects of Visual Nudges on Target Choices

### Equation 2 and Table 3

```{r table3}
# each version is compared with the same participants' baseline round, both scored
# against the version's target action; decoy: target set vs control set (outcome Buy)
var_of <- list(framing_text   = c(up = "framing70",     down = "framing30"),
               framing_visual = c(up = "framinggreen",  down = "framingred"),
               rare_event     = c(up = "scarcityInc",   down = "scarcityDec"),
               herd           = c(up = "herdbuy",       down = "herdsell"),
               anchoring      = c(up = "anchoringhigh", down = "anchoringlow"))
single <- c("middle", "status_quo", "time_limit")
hits_target <- function(action, target) as.integer(!is.na(target) & !is.na(action) &
  (action == target | (target == "BUY_SELL" & action %in% c("BUY", "SELL"))))
own <- function(v, d, tgt) rbind(
  data.frame(pid = d$participant_id, v = v, k = 1L, y = hits_target(d$action, tgt)),
  data.frame(pid = d$participant_id, v = v, k = 0L, y = hits_target(d$baseline_action, tgt)))
CS <- list()
for (c in names(var_of)) for (dir in c("up", "down")) { e <- var_of[[c]][[dir]]
  d <- long[long$experiment == e & long$action %in% bhs & !is.na(long$baseline_action), ]
  CS[[e]] <- own(e, d, if (dir == "up") "BUY" else "SELL") }
for (c in single) { d <- long[long$condition == c & !is.na(long$baseline_action), ]
  CS[[c]] <- own(c, d, as.character(d$target)) }
dz <- long[long$condition %in% c("decoy_no", "decoy_yes") & long$action %in% bhs, ]
CS[["decoy"]] <- data.frame(pid = dz$participant_id, v = "decoy",
                            k = as.integer(dz$condition == "decoy_yes"), y = as.integer(dz$action == "BUY"))
CC <- merge(do.call(rbind, CS), cov, by.x = "pid", by.y = "participant_id", all.x = TRUE)
CC$v <- factor(CC$v, levels = names(CS))

# column (1): each contrast on its own
c1 <- do.call(rbind, lapply(names(CS), function(v) { ct <- clp(lm(y ~ k, CS[[v]]), ~pid)
  data.frame(version = v, est = 100 * ct["k", 1], se = 100 * ct["k", 2], p = ct["k", 4],
             n = length(unique(CS[[v]]$pid[CS[[v]]$k == 1]))) }))
# column (2): one stacked model with contrast-specific intercepts and effects, shared covariates
m2 <- lm(y ~ 0 + v + v:k + risk + chartc + invested, CC); c2 <- clp(m2, ~pid)
k2 <- paste0("v", c1$version, ":k")
t3 <- data.frame(Version = c1$version,
                 `(1)` = sprintf("%.1f%s", c1$est, star(c1$p)), SE1 = sprintf("(%.1f)", c1$se),
                 `(2)` = sprintf("%.1f%s", 100 * c2[k2, 1], star(c2[k2, 4])), SE2 = sprintf("(%.1f)", 100 * c2[k2, 2]),
                 n = c1$n, check.names = FALSE)
t3
c(decoy_target_set = sum(dz$condition == "decoy_yes"), decoy_control_set = sum(dz$condition == "decoy_no"))

# Panel C: shared covariates, column (2)
cv <- c("risk", "chartc", "investedYes")
data.frame(Term = c("Risk tolerance (1-5)", "Chart comfort (1-5)", "Invested before (Yes)"),
           Estimate = sprintf("%.1f%s", 100 * c2[cv, 1], star(c2[cv, 4])), SE = sprintf("%.1f", 100 * c2[cv, 2]))
c(contrasts = length(CS), participants = length(unique(CC$pid)), stacked_observations = nobs(m2))
```

### Figure 3a: 90% and 95% Confidence Intervals

```{r fig3a}
f3a <- transform(c1, lo90 = est - 1.645 * se, hi90 = est + 1.645 * se, lo95 = est - 1.96 * se, hi95 = est + 1.96 * se)
f3a[, -1] <- round(f3a[, -1], 3)
f3a
c(ci90_includes_zero = sum(f3a$lo90 <= 0 & f3a$hi90 >= 0), ci95_excludes_zero = sum(f3a$lo95 > 0 | f3a$hi95 < 0))
```

## 4.3 AI Assistance as a Choice Architecture Moderator

### Equation 3 and Table 4

```{r table4}
d <- long[long$condition != "time_limit" & long$action %in% bhs, ]
d <- merge(d, cov, by = "participant_id", all.x = TRUE)
d$ai <- relevel(factor(d$ai_condition), ref = "NO_AI")
dp <- d[d$condition != "status_quo", ]                 # Time Limit and Inaction Friction excluded
m1 <- clp(lm(on_target ~ ai + factor(experiment), dp), dp$participant_id)
m2 <- clp(lm(on_target ~ ai + factor(experiment) + risk + chartc + invested, dp), dp$participant_id)
og <- clp(glm(on_target ~ ai + factor(experiment), binomial, dp), dp$participant_id)
ppci <- function(ct, k) sprintf("%.1f%s [%.1f, %.1f]", 100 * ct[k, 1], star(ct[k, 4]),
                                100 * (ct[k, 1] - 1.96 * ct[k, 2]), 100 * (ct[k, 1] + 1.96 * ct[k, 2]))
orci <- function(ct, k) sprintf("%.2f [%.2f, %.2f]", exp(ct[k, 1]), exp(ct[k, 1] - 1.96 * ct[k, 2]), exp(ct[k, 1] + 1.96 * ct[k, 2]))
ks <- paste0("ai", c("NEUTRAL_AI", "BIASED_AI", "DEBIASED_AI"))
data.frame(AI = arms[-1], `(1) pp [95% CI]` = ppci(m1, ks), `(2) + covariates` = ppci(m2, ks),
           `Odds ratio [95% CI]` = orci(og, ks), check.names = FALSE)
nrow(dp)

# raw share of target-action choices by AI group (%)
round(100 * tapply(dp$on_target, dp$ai_condition, mean), 1)
```

### Figure 3b: Biased AI vs No AI by Condition

```{r fig3b}
cs <- c("decoy_no", "decoy_yes", "middle", "rare_event", "framing_text", "framing_visual", "herd", "anchoring")
f3b <- do.call(rbind, lapply(cs, function(cn) { dc <- d[d$condition == cn, ]
  f <- if (nlevels(droplevels(dc$experiment)) > 1) on_target ~ ai + factor(experiment) else on_target ~ ai
  ct <- clp(lm(f, dc), dc$participant_id)
  data.frame(condition = cn, est = 100 * ct["aiBIASED_AI", 1], se = 100 * ct["aiBIASED_AI", 2],
             p = ct["aiBIASED_AI", 4], n = sum(dc$ai %in% c("NO_AI", "BIASED_AI"))) }))
f3b <- transform(f3b, lo95 = est - 1.96 * se, hi95 = est + 1.96 * se)
f3b[, -1] <- round(f3b[, -1], 3); f3b

# rounds per direction (biased and no-assistant groups)
sapply(unlist(var_of), function(e) sum(d$experiment == e & d$ai %in% c("NO_AI", "BIASED_AI")))
```

## 4.4 Decomposing the Nudge Effects

### Equation 4 and Table 5

```{r table5}
mnud <- long[long$action %in% bhs, c("participant_id", "experiment", "action")]
names(mnud)[2] <- "version"
mbas <- data.frame(participant_id = wide$participant_id, version = "baseline", action = wide$baseline_action)
MM <- rbind(mnud, mbas)
MM$action  <- relevel(factor(MM$action), ref = "HOLD")
MM$version <- relevel(factor(MM$version), ref = "baseline")
mfit <- multinom(action ~ version, MM, trace = FALSE); mcf <- coef(mfit)

# participant-clustered bootstrap (participants resampled)
set.seed(20261005); B <- 999
ids <- unique(MM$participant_id); byid <- split(seq_len(nrow(MM)), MM$participant_id)
boot <- replicate(B, { s <- sample(ids, length(ids), replace = TRUE)
  bm <- MM[unlist(byid[s], use.names = FALSE), ]
  f <- tryCatch(multinom(action ~ version, bm, trace = FALSE, maxit = 500), error = function(e) NULL)
  if (is.null(f) || !identical(dim(coef(f)), dim(mcf))) matrix(NA, nrow(mcf), ncol(mcf)) else coef(f) }, simplify = "array")
mse <- apply(boot, c(1, 2), sd, na.rm = TRUE); dimnames(mse) <- dimnames(mcf)
mp  <- 2 * (1 - pnorm(abs(mcf / mse)))
vers <- c("framing70", "framing30", "framinggreen", "framingred", "scarcityInc", "scarcityDec", "herdbuy", "herdsell",
          "anchoringhigh", "anchoringlow", "decoyNo", "decoyYes", "middle", "statusquo", "timelimit")
kv <- paste0("version", vers)
data.frame(Version = vers,
           `Buy vs Hold (OR)`  = sprintf("%.2f%s", exp(mcf["BUY", kv]),  star(mp["BUY", kv])),
           `Sell vs Hold (OR)` = sprintf("%.2f%s", exp(mcf["SELL", kv]), star(mp["SELL", kv])),
           `p Buy` = round(mp["BUY", kv], 3), `p Sell` = round(mp["SELL", kv], 3), check.names = FALSE)
c(decisions = nrow(MM), participants = length(ids), replicates = sum(!is.na(boot[1, 1, ])))
```

### Choice Shares by Version (Decoy and Middle Option)

```{r shares}
shares <- function(e) { x <- long$action[long$experiment == e]
  c(n = length(x), Buy = 100 * mean(x == "BUY"), Hold = 100 * mean(x == "HOLD"), Sell = 100 * mean(x == "SELL")) }
round(t(sapply(c(vers[1:13]), shares)), 1)
```

# 5. Robustness and Heterogeneity Analysis

## 5.1 Treatment Effect Heterogeneity

### 5.1.1 Heterogeneity by Individual Differences (Table A6)

```{r tableA6}
# trait groups (group 1 vs group 0), all reported before the task
pm <- data.frame(participant_id = wide$participant_id,
  invested = as.integer(wide$investment_exp == "Yes"),
  news_hi  = as.integer(wide$news_frequency %in% c("Daily", "Weekly", "Monthly")),
  risk_hi  = as.integer(wide$risk_tolerance  >= 4),
  chart_hi = as.integer(wide$chart_comfort   >= 4),
  quick_hi = as.integer(wide$quick_decisions >= 4),
  risk = wide$risk_tolerance, chartc = wide$chart_comfort,
  trust = wide$ai_trust, pred = wide$ai_predictable, comf = wide$ai_comfort,
  eng = wide$total_ai_requests, aic = wide$session_ai_condition)
MODS <- c("invested", "news_hi", "risk_hi", "chart_hi", "quick_hi")
sapply(pm[MODS], function(m) c(n = sum(m), pct = round(100 * mean(m))))

CH <- merge(CC[, c("pid", "v", "k", "y")], pm[, c("participant_id", MODS)], by.x = "pid", by.y = "participant_id")
hz <- do.call(rbind, lapply(levels(CC$v), function(v) do.call(rbind, lapply(MODS, function(m) {
  s <- CH[CH$v == v, ]; s$m <- s[[m]]; ct <- clp(lm(y ~ k * m, s), s$pid)
  data.frame(effect = v, trait = m, est = 100 * ct["k:m", 1], se = 100 * ct["k:m", 2], p = ct["k:m", 4], n_obs = nrow(s)) }))))

# biased AI x trait, in the Table 4 column (1) model
ai <- long[!(long$condition %in% c("time_limit", "status_quo")) & long$action %in% bhs, ]
ai <- merge(ai, pm, by = "participant_id", all.x = TRUE)
ai$ai <- relevel(factor(ai$ai_condition), ref = "NO_AI")
ha <- do.call(rbind, lapply(MODS, function(m) { a <- ai; a$m <- a[[m]]
  ct <- clp(lm(on_target ~ ai * m + factor(experiment), a), a$participant_id)
  data.frame(effect = "biased_ai", trait = m, est = 100 * ct["aiBIASED_AI:m", 1], se = 100 * ct["aiBIASED_AI:m", 2],
             p = ct["aiBIASED_AI:m", 4], n_obs = nrow(a)) }))
H <- rbind(hz, ha)
H$q_BH <- p.adjust(H$p, "BH")
H$cell <- sprintf("%.1f%s", H$est, star(H$p))
tA6 <- reshape(H[, c("effect", "trait", "cell")], idvar = "effect", timevar = "trait", direction = "wide")
tA6
unique(H[, c("effect", "n_obs")])
c(interactions = nrow(H), p_below_05 = sum(H$p < .05), expected_by_chance = .05 * nrow(H),
  q_below_05 = sum(H$q_BH < .05), smallest_q = round(min(H$q_BH), 3))
H[order(H$p)[1:5], ]
```

### 5.1.2 Susceptibility to AI Assistance (Table 6)

```{r table6}
# moderators standardized across participants in the assistant groups
onai <- pm$aic != "NO_AI"
for (m in c("trust", "pred", "comf", "eng")) { z <- rep(NA_real_, nrow(pm))
  z[onai] <- (pm[[m]][onai] - mean(pm[[m]][onai], na.rm = TRUE)) / sd(pm[[m]][onai], na.rm = TRUE)
  ai[[paste0("z_", m)]] <- z[match(ai$participant_id, pm$participant_id)] }
at <- ai[ai$ai_condition != "NO_AI", ]
at$ai <- relevel(droplevels(factor(at$ai_condition)), ref = "BIASED_AI")
ppse <- function(ct, k) sprintf("%.1f%s (%.1f)", 100 * ct[k, 1], star(ct[k, 4]), 100 * ct[k, 2])
do.call(rbind, lapply(c("trust", "pred", "comf", "eng"), function(m) {
  a <- at; a$z <- a[[paste0("z_", m)]]; a <- a[!is.na(a$z), ]
  ct <- clp(lm(on_target ~ ai * z + factor(experiment), a), a$participant_id)
  data.frame(Moderator = m, `Biased: slope` = ppse(ct, "z"), `Debiasing x moderator` = ppse(ct, "aiDEBIASED_AI:z"),
             `Neutral x moderator` = ppse(ct, "aiNEUTRAL_AI:z"), Participants = length(unique(a$participant_id)),
             Decisions = nrow(a), check.names = FALSE) }))
```

## 5.2 Methodological Robustness and Sensitivity Checks

### 5.2.1 Alternative Econometric Specifications (Table A7)

```{r tableA7}
# same specification as LPM, logit, and probit; average marginal effects with
# participant-clustered delta-method standard errors
ame_dm <- function(fit, rows, d1, d0, V) {
  tt <- delete.response(terms(fit)); b <- coef(fit); ok <- !is.na(b)
  X1 <- model.matrix(tt, d1[rows, ], xlev = fit$xlevels)[, ok, drop = FALSE]
  X0 <- model.matrix(tt, d0[rows, ], xlev = fit$xlevels)[, ok, drop = FALSE]
  if (inherits(fit, "glm")) { li <- fit$family$linkinv; me <- fit$family$mu.eta
    e1 <- drop(X1 %*% b[ok]); e0 <- drop(X0 %*% b[ok])
    est <- mean(li(e1) - li(e0)); g <- colMeans(me(e1) * X1 - me(e0) * X0)
  } else { est <- mean(drop((X1 - X0) %*% b[ok])); g <- colMeans(X1 - X0) }
  se <- sqrt(drop(t(g) %*% V[ok, ok] %*% g)); c(est = 100 * est, se = 100 * se, p = 2 * pnorm(-abs(est / se))) }
fmt <- function(r) sprintf("%.1f%s (%.1f)", r[["est"]], star(r[["p"]]), r[["se"]])

# nudge effects: Table 3, column (2)
fn <- y ~ 0 + v + v:k + risk + chartc + invested
fits <- list(LPM = lm(fn, CC), Logit = glm(fn, binomial("logit"), CC), Probit = glm(fn, binomial("probit"), CC))
C1 <- CC; C1$k <- 1L; C0 <- CC; C0$k <- 0L
a7n <- do.call(rbind, lapply(levels(CC$v), function(v) { rows <- which(CC$v == v)
  r <- sapply(fits, function(f) fmt(ame_dm(f, rows, C1, C0, vcovCL(f, cluster = CC$pid))))
  data.frame(Effect = v, t(r), N = length(rows)) }))

# AI effects: Table 4, column (2)
fa <- on_target ~ ai + factor(experiment) + risk + chartc + invested
afits <- list(LPM = lm(fa, ai), Logit = glm(fa, binomial("logit"), ai), Probit = glm(fa, binomial("probit"), ai))
A0 <- ai; A0$ai <- factor("NO_AI", levels = levels(ai$ai))
a7a <- do.call(rbind, lapply(c("NEUTRAL_AI", "BIASED_AI", "DEBIASED_AI"), function(g) {
  A1 <- ai; A1$ai <- factor(g, levels = levels(ai$ai))
  r <- sapply(afits, function(f) fmt(ame_dm(f, seq_len(nrow(ai)), A1, A0, vcovCL(f, cluster = ai$participant_id))))
  data.frame(Effect = g, t(r), N = nrow(ai)) }))
rbind(a7n, a7a)

# fitted values of the linear probability models
fitted_all <- c(fitted(lm(y ~ 0 + v + v:k, CC)), fitted(lm(y ~ 0 + v + v:k + risk + chartc + invested, CC)),
                fitted(lm(on_target ~ ai_condition + factor(experiment), dp)),
                fitted(lm(on_target ~ ai_condition + factor(experiment) + risk + chartc + invested, dp)))
round(range(fitted_all), 2)
```

### 5.2.2 Round Order and Carry-Over Effects

```{r round-order}
ord <- long[long$condition != "time_limit", ]
ct <- clp(lm(on_target ~ factor(condition) + round, ord), ord$participant_id)
c(pp_per_round = 100 * ct["round", 1], se = 100 * ct["round", 2], p = ct["round", 4], decisions = nrow(ord))

# final round among participants whose block did not include the time limit
has_tl <- tapply(long$condition == "time_limit", long$participant_id, any)
fr5 <- long[long$participant_id %in% names(which(!has_tl)), ]
fr5$r5 <- as.integer(fr5$round == 5); fr5$active <- as.integer(fr5$action %in% c("BUY", "SELL"))
o2 <- clp(lm(active ~ factor(condition) + r5, fr5), fr5$participant_id)
c(participants = length(unique(fr5$participant_id)), pp_round5_active = 100 * o2["r5", 1], p = o2["r5", 4])
```

# 6. Discussion

## 6.1 Inaction Friction by AI Group

```{r inaction-friction}
sq <- CC[CC$v == "status_quo", ]
sq$ai <- wide$session_ai_condition[match(sq$pid, wide$participant_id)]
if_eff <- function(s) { ct <- clp(lm(y ~ k, s), s$pid)
  c(pp = 100 * ct["k", 1], se = 100 * ct["k", 2], p = ct["k", 4], participants = sum(s$k == 1)) }
rbind(all = if_eff(sq), biased_ai = if_eff(sq[sq$ai == "BIASED_AI", ]),
      other_groups = if_eff(sq[sq$ai != "BIASED_AI", ]))
```

# Appendix B. Baseline Choice versus Nudge-Round Choice (Table A1)

```{r tableA1}
for (e in c("framing70", "framing30", "framinggreen", "framingred", "scarcityInc", "scarcityDec", "decoyYes", "decoyNo")) {
  dd <- long[long$experiment == e, ]
  cat("\n", e, "\n"); print(addmargins(table(baseline = factor(dd$baseline_action, levels = bhs),
                                             nudge = factor(dd$action, levels = bhs)), 2)) }
```

# Appendix C. Experimental Randomization Protocol and BIBD Parameters (Table A2)

```{r tableA2}
cond_order <- c("decoy_no", "decoy_yes", "middle", "rare_event", "framing_text", "framing_visual", "herd",
                "anchoring", "status_quo", "time_limit")
addmargins(table(factor(long$condition, levels = cond_order), factor(long$ai_condition, levels = names(arms))), 2)

sets <- tapply(as.character(long$condition), long$participant_id, function(x) paste(sort(unique(x)), collapse = "+"))
full <- sets[lengths(strsplit(sets, "[+]")) == 5]
blk  <- table(full)
pairs <- combn(cond_order, 2)
shared <- apply(pairs, 2, function(p) sum(vapply(strsplit(full, "[+]"), function(s) all(p %in% s), logical(1))))
c(blocks = length(blk), participants_per_block_min = min(blk), participants_per_block_max = max(blk),
  blocks_with_13 = sum(blk == 13), pair_participants_min = min(shared), pair_participants_max = max(shared))
```

# Appendix E. Sample Characteristics, Decision Times, and Process Measures

### Table A3

```{r tableA3}
blockc <- function(vec, levels) { k <- vapply(levels, function(l) sum(vec == l, na.rm = TRUE), integer(1))
  data.frame(Category = levels, N = k, Pct = round(100 * k / length(vec), 1), row.names = NULL) }
blockc(wide$age_grp, c("18-24", "25-34", "35-44", "45+"))
blockc(wide$gender, c("Female", "Male", "Prefer not to say"))
blockc(wide$nationality_grp, c("Armenian", "Other"))
blockc(wide$education_grp, c("High school or Bachelor's", "Master's", "PhD"))
blockc(wide$field, c("STEM", "Business / Economics", "Social Sciences", "Arts / Humanities", "Other"))
blockc(wide$employment, c("Bachelor/Master student", "PhD student", "Researcher / Lecturer", "Employed",
                          "Self-employed / Business owner", "Unemployed", "Other"))
blockc(wide$investment_exp, c("Yes", "No"))
blockc(wide$news_frequency, c("Daily", "Weekly", "Monthly", "Rarely", "Never"))
vars <- c("years_investing", "risk_tolerance", "chart_comfort", "quick_decisions", "round2_confidence",
          "round4_confidence", "ai_trust", "ai_predictable", "ai_comfort")
t(sapply(vars, function(v) { s <- num_sum(wide[[v]]); c(Mean = round(s[["Mean"]], 2), SD = round(s[["SD"]], 2), n = s[["n"]]) }))
```

### Table A4

```{r tableA4}
round(rbind(
  `Total session duration (min)`     = num_sum(wide$completion_time_min),
  `Baseline decision (s)`            = num_sum(wide$baseline_sec),
  `Treatment-round decision (s)`     = num_sum(nt$decision_sec),
  `  rounds with an AI query (s)`    = num_sum(nt$decision_sec[nt$asked_ai_round]),
  `  rounds without an AI query (s)` = num_sum(nt$decision_sec[!nt$asked_ai_round]),
  `AI messages per session (count)`  = num_sum(wide$total_ai_requests),
  do.call(rbind, lapply(setNames(names(arms), paste("Session duration (min),", arms)),
                        function(a) num_sum(wide$completion_time_min[wide$session_ai_condition == a])))), 1)
```

### Process Measures by AI Group

```{r process}
pmed <- tapply(nt$decision_sec, nt$participant_id, median, na.rm = TRUE)
parm <- factor(wide$session_ai_condition[match(names(pmed), wide$participant_id)], levels = names(arms))
conf <- rowMeans(cbind(wide$round2_confidence, wide$round4_confidence), na.rm = TRUE)
tr   <- wide$ai_trust; sub <- ai_f != "NO_AI"
rbind(median_decision_sec = tapply(pmed, parm, median, na.rm = TRUE),
      mean_confidence     = tapply(conf, ai_f, mean, na.rm = TRUE),
      mean_trust          = tapply(tr, ai_f, mean, na.rm = TRUE))
c(kruskal_decision_time = kruskal.test(pmed ~ parm)$p.value,
  anova_confidence      = summary(aov(conf ~ ai_f))[[1]][["Pr(>F)"]][1],
  anova_trust           = summary(aov(tr[sub] ~ droplevels(ai_f[sub])))[[1]][["Pr(>F)"]][1])

# biased vs neutral and biased vs debiasing: Welch t-test and Wilcoxon rank-sum, Holm-adjusted
pw <- sapply(c("NEUTRAL_AI", "DEBIASED_AI"), function(a) { x <- tr[ai_f == "BIASED_AI"]; y <- tr[ai_f == a]
  c(welch = t.test(x, y)$p.value, wilcoxon = suppressWarnings(wilcox.test(x, y, exact = FALSE)$p.value)) })
rbind(welch_holm = p.adjust(pw["welch", ], "holm"), wilcoxon_holm = p.adjust(pw["wilcoxon", ], "holm"))
```

# Appendix F. Directional Asymmetry of the Paired Nudges (Table A5)

```{r tableA5}
tA5 <- cbind(round(t(sapply(unlist(var_of), shares)), 1),
             f3a[match(unlist(var_of), f3a$version), c("est", "lo95", "hi95", "p")])
tA5
```
